---
title: "Completed Tasks for Mattoni 1873"
author: "Suslin Egor"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
vignette: >
  %\VignetteIndexEntry{Completed Tasks for Mattoni 1873}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This is RMarkDown presentation of my results made for Mattoni 1873 company.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
getwd()
setwd("F:/folder")
library(readxl)
library(sqldf)
my_data = read_excel("task1_data.xlsx")
```
# Task 1: MS Excel formulas
## First Question
###1. Kolik se prodalo litrů (Volume in 1000 LTR) produktu FUZETEA-GR.TEA LIME&MINT 1.5L PB v CZ Supermarkets v roce 2014?
```{r}
V1_fuzz = sqldf('SELECT * from my_data WHERE ITEM = "FUZETEA-GR.TEA LIME&MINT 1.5L PB" AND MARKET = "CZ Hypermarkets"' )
Answer1 = V1_fuzz[3,9]
### ANSWER : 108.3073
```
Answer for the question number one is `r Answer1`


## Second Question 
### 2. Jaká byla průměrná cena produktu AQUILA-PRVNI VODA KOJENECKA 1.5L PB NS K v CZ Hypermarkets letech 2014, 2015, 2016?
```{r}
AVG_AQ = sqldf('SELECT * from my_data WHERE ITEM = "AQUILA-PRVNI VODA KOJENECKA 1.5L PB NS K" AND MARKET = "CZ Hypermarkets"' )
Total = AVG_AQ[4,]
Answer2_2014 = AVG_AQ[4,9]
Answer2_2015 = AVG_AQ[4,10]
Answer2_2016 = AVG_AQ[4,11]
```
Answer for the question number two:  
|2014 | `r Answer2_2014`|  
|2015 | `r Answer2_2015`|  
|2016 | `r Answer2_2016`|  


## Third Question
### 3. Kolik se prodalo v CZK (Value in 1 000 000 CZK) produktu 7UP-1L PB na CZ Petrol Stations v roce 2015?

```{r}
CZK_7UP = sqldf('SELECT * FROM my_data WHERE ITEM = "7UP-1L PB" AND MARKET = "CZ Petrol Stations"')
Answer3 = CZK_7UP[2,10]
```
```{r, include=FALSE}
excel_for_task3 = "=SUMIFS(J2:J12381;H2:H12381;M4;F2:F12381;M5;G2:G12381;M6)"
```
Answer : `r Answer3`  
Formula : `r excel_for_task3`, where M4 = Value (in 1 000 000 CZK), M5 = 7UP-1L PB, M6 = CZ Petrol Stations


## Four Question
### 4. Kolik se prodalo kusů (Units in 1000 PCS) 0.5L PET lahví ve WATER kategorii během roku 2014?

```{r}
names(my_data)[names(my_data) == 'PACKAGE TYPE'] <- 'PACKAGE_TYPE'
PET_2014 = sqldf('SELECT * FROM my_data WHERE CATEGORY = "TOTAL WATER" AND PACKAGE_TYPE = "BOTTLE PET" AND SIZE = "0.5L" AND FACT = "Units (in 1000 PCS)"')
Answer4 = sum(PET_2014[, "2014.0"]/2) ### In 1000 PCS
```
```{r, include=FALSE}
excel_for_task4 = "=SUMIFS(I2:I12381;H2:H12381;P4;E2:E12381;P5;D2:D12381;P7;A2:A12381;P6;G2:G12381;P9)"
```
Answer : `r Answer4`  
Formula : `r excel_for_task4`, where P4 = Units (in 1000 PCS), P5 = 0.5L, P6 = TOTAL WATER, P7 = BOTTLE PET, P9 = CZ Total


# Task 2: Dashboards and Q3, Q4 Market Analyze
## Dashboards :  

I created 4 different dashboards  
2 of them are with Mattoni Company presented Value and Volume.
And 2 of them of all companies. I made it only to compare and better visualization.  
Main Mattoni Dashboards:  
  Value : https://egorsuslindatascience.shinyapps.io/Value_Mattoni/?_ga=2.49230179.457610995.1632325667-1065273964.1631210772   
  Volume: https://egorsuslindatascience.shinyapps.io/Volume_Mattoni/?_ga=2.49230179.457610995.1632325667-1065273964.1631210772  
Dashboard of all Companies :  
  Value : https://egorsuslindatascience.shinyapps.io/All_Value/?_ga=2.120533709.457610995.1632325667-1065273964.1631210772   
  Volume: https://egorsuslindatascience.shinyapps.io/All_Volume/?_ga=2.49230179.457610995.1632325667-1065273964.1631210772  

## Market Analyze : 

I calculated total market shares of Mattoni 1873. I summarized Volume of LTRS for Q3 and Q4 in 2019 and divide it by All Volume of LTRS from all brands, which were presented in provided Data set.  
Here is my calculations in R. I made the same for Value to compare the results.
```{r, include=TRUE}
source(file = "preprocc_task2.r")
###q3 and q4 for volume
#q3
q3_all = sum(All_Volume[, 21])
q3_mattoni = sum(Mattoni1873_Volume[, 21])
q3 = (q3_mattoni/q3_all) * 100
#q4
q4_mattoni = sum(Mattoni1873_Volume[, 22])
q4_all = sum(All_Volume[, 22])
q4 = (q4_mattoni/q4_all) * 100

#-----------------------------------------------
#q3 and q4 value % from the whole water market in CZ
q3_value_all = sum(All_Value[, 21])
q3_value_mattoni = sum(Mattoni1873_Value[, 21])  
q3_value = (q3_value_mattoni/q3_value_all) * 100

q4_value_all = sum(All_Value[, 22])
q4_Value_mattoni = sum(Mattoni1873_Value[, 22])
q4_value = (q4_Value_mattoni/q4_value_all) * 100

```
q3_all - all volume Q3, q3_mattoni - Mattoni volume Q3, q3 - Mattoni market shares in Q3  
q4_all - all volume Q4, q4_mattoni - Mattoni volume Q4, q4 - Mattoni market shares in Q4  
  
q3_value_all - all value Q3, q3_value_mattoni - mattoni value Q3, q3_value - market shares in Q3  
q4_value_all - all value Q4, q4_value_mattoni - mattoni value Q4, q4_value - market shares in Q4  
Results:  
  Market Share of Mattoni 1873 in Q3 : `r q3` (Calculated with Volume)  
  Market Share of Mattoni 1873 in Q4 : `r q4` (Calculated with Volume)  
  
  Market Share of Mattoni 1873 in Q3 : `r q3_value` (Calculated with Value)  
  Market Share of Mattoni 1873 in Q4 : `r q4_value` (Calculated with Value)  

The results for Volume and Value are really close.
  

### Conclusion:  

Mattoni 1873 have showed stability during Q3 and Q4 in 2019. We have really close results.  
I mentioned small difference between q3 = `r q3` < q3_value `r q3_value` and q4 = `r q4` < q4_value `r q4_value`. I think this is due to the fact that Mattoni brands have a bit higher prices in the market, so they are getting higher % of water market share in Volume of amount of all purchased water in provided Data Base.

# Thank you for time and the opportunity to work with problems like this.
